---
title: "TP2 - Exercise 4"
author: "Manuela Giansante and Lucia Camenisch"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    toc: true # creating a table of contents (toc)
    toc_float: 
      collapsed: false # toc does not collapse and is shown as a sidebar (toc_float)
    number_sections: true # document sections are numbered
    theme: cosmo
---

```{=html}
<style>
body{
  color: #630000;
  background-color: #FBF1D2;
}
pre{
  background-color: #FFF7ED;
}
pre:not([class]){
  background-color: #EBE7AA;
}
.toc-content{
  padding-left: 10px;
  padding-right: 10px;
}
.col-sm-8 {
  width: 75%;
}
code {
  color: #333333;
  background-color: #FFF7ED;
}
</style>
```
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, fig.align = "center")
```

```{r, warning=FALSE, message=FALSE}
# We load the necessary libraries
library(data.table)
library(ggplot2)
library(kableExtra)
library(dplyr)
```

```{r}
panels <- fread("Case_Stud_ I.csv")

# This dataset contains the following columns:
# Number of Solar Panels
# Manufacturing Costs
```

# PART I

## Use an electronic spreadsheet to plot the data and draw a scatter plot.

```{r}
ggplot(panels, aes(x = number_of_solar_panels, y = manufacturing_cost)) +
  geom_point() +
  xlab("Number of Solar Panels Produced") +
  ylab("Manufactoring Costs")+
  ggtitle("Manufactoring Costs per Units Produced")+
  theme_light()
```

We observe that as the amount of units produced cumulatively increases the costs of manufacturing per unit decline. The gained experience reduces the marginal costs with a constant rate, which is the learning rate.

## Does the multiplicative learning model which assumes the following relationship: $Y = AX^b$ apply to this data set?

The data as plotted out above follows an exponential shape, the suggested non linear relationship applies.

The plot above can be interpreted as an experience curve, given that we are considering cumulative production and manufacturing cost per batch of 100 panels produced.

## Make an appropriate transformation of the data and redo the plot with the transformed data.

```{r}
panels_log = log(panels)
head(panels_log) %>% kbl() %>% kable_styling("hover", full_width = F)
```

```{r}
ggplot(panels_log, aes(x = number_of_solar_panels, y = manufacturing_cost)) +
  geom_point() +
  xlab("Log(Number of Solar Panels Produced)") +
  ylab("Log(Manufactoring Costs)")+
  ggtitle("Log-log Plot: Manufactoring Costs per Units Produced")+
  theme_light()
```

By logging the data the relationship $Y=AX^{b}$ becomes $\log(Y)=\log(A)+b\log(X)$, that is now a linear relationship in fact the plotted data no longer follows an exponential shape. In our case the response variable is the cost and the predictor is the number of produced panels.

# PART II

## Conduct a linear regression with the transformed data.

```{r}
LinReg = lm(manufacturing_cost ~ number_of_solar_panels, data = panels_log)
summary(LinReg)

```

In the context of a linear regression the intercept estimate $\beta_0$ is the $\log(A)$ we mentioned above, and the coefficient of the `number_of_solar_panels` $\beta_1$ is the $b$ constant preceading $\log(X)$.

Both coefficients are significant and the adjusted $R^2$ is quite high, the model does a good job at explaining the variation in the data.

```{r}
plot(LinReg)
```

**Residuals vs Fitted Values plot**

The residuals are scattered around the 0 line suggesting that the relationship between response and predictor is linear.

There is an horizontal band around the 0 line, but the logarithm shifted the cloud of point to the left appearing therefore less uniform.

**Q-Q plot**

The residuals appear normally distributed and they hug the diagonal line without forming any curving shaping which would indicate a violation of the normal distribution and independence assumption regarding errors.

## Interpret the results of the regression analysis. How well does the model explain the data? What is the learning rate that applies in this case?

```{r}
# retrieving the coefficients as computed
beta = LinReg$coefficients
beta %>% kbl(col.names = "Coefficients") %>% kable_styling("hover", full_width = F)
```

```{r}
ggplot(panels_log, aes(x = number_of_solar_panels, y = manufacturing_cost)) +
  geom_point() +
  geom_abline(intercept = beta[1], slope = beta[2], color = "red") +
  xlab("Log(Number of Solar Panels Produced)") +
  ylab("Log(Manufactoring Costs)")+
  ggtitle("Log-log Plot with Fitted Line: Manufactoring Costs per Units Produced")+
  theme_light()
```

As previously seen the adjusted $R^2$ indicated that the fitted model explains 94% of the variations in the manufacturing costs. The fit of the model is satisfying.


We retrieve coefficients $A$ and $b$ from the linear regression coefficients as we mentioned before.
$$
\begin{align}
A & = \log(\beta_0) \\
b &= \beta_1
\end{align}
$$


```{r}
# Retrieving the coefficients
A = as.numeric(exp(beta[1]))
b = as.numeric(beta[2])
```


The learning rate is defined as follows:

"Each duplication of the *accumulated output of a product* ($X$) in a certain period of time decreases the *inflation-adjusted marginal cost* ($Y$) with a constant percentage, the *learning rate* ($l$)."

Translating this expression in a mathematical equation, we can thus retrieve a formula for the learning rate $l$. It is equal to
$$l = 1 - \dfrac{\tilde Y}{Y}$$
where $Y$ is the cost for an accumulated output $X$ and $\tilde Y$ is the cost for double that output, i.e. $2X$.

Using our model's function:

$$
\begin{align}
Y &= A X^b \\ 
\tilde Y &= A (2X)^b
\end{align}
$$
Thus,

$$
\begin{align}
l &= 1 - \dfrac{\tilde Y}{Y} \\ 
&= 1 - \dfrac{A (2X)^b}{A X^b} \\
&= 1 - 2^b
\end{align}
$$


```{r}
# as defined the learning rate is 1-2^b
l = 1-2^b
```



```{r}
df<- data.frame(A,b,l)
df%>% kbl() %>% kable_styling("hover", full_width = F)
```

# PART III

## Use the experience curve estimate from the regression model to calculate the expected average manufacturing cost per solar panel for the 400 solar panels that would be produced.

We generate the data for the new produced batches up to 5000 units.

```{r}
# Data Generation
panels_pred =  data.table(number_of_solar_panels = seq(100, 5000, 100))
panels_pred[, manufacturing_cost := A*number_of_solar_panels^b]# computation of response variable

```

```{r}
ggplot(panels, aes(x = number_of_solar_panels, y = manufacturing_cost)) +
  geom_point() +
  geom_point(data=panels_pred[c(47:50),], color="blue")+
  geom_line(data = panels_pred, aes(x = number_of_solar_panels, y = manufacturing_cost), color = "red") +
  xlab("Number of Solar Panels Produced") +
  ylab("Manufactoring Costs")+
  ggtitle("Real Data and predicted Data: Manufactoring Costs per Units Produced")+
  theme_light()
```

The red line plots the predicted values for the all the produced batches, in blue the 400 panels of interest.
In black we have the collected data.

```{r}
# average manufacturing cost per solar panel for 4700, 4800, 4900 and 5000:
mean(panels_pred$manufacturing_cost[47:50])
# average unit cost for the collected data before the placement of the bid:
mean(panels$manufacturing_cost)
```

# PART IV

## Calculate a 95% confidence interval for the average manufacturing cost per solar panel for the panels produced for Switzerland by using the lower and upper bounds of the confidence interval estimate for the experience parameter.

```{r}
CI = confint(LinReg)
CI
```

```{r}
b_lower = CI[2,1]# lower bounds
b_upper = CI[2,2]# upper bounds
b_lower
b_upper
```

```{r}
#Response recomputed with bounds values
panels_pred[, lower := A*number_of_solar_panels^b_lower]
panels_pred[, upper := A*number_of_solar_panels^b_upper]
panels_pred[1:22, 3:4] = NA # collected data
```

```{r}
ggplot(panels, aes(x = number_of_solar_panels, y = manufacturing_cost)) +
  geom_point() +
  geom_line(data = panels_pred, aes(x = number_of_solar_panels, y = manufacturing_cost), color = "red") +
  geom_ribbon(data = panels_pred, aes(ymin = lower, ymax = upper), alpha = 0.3, color = NA, fill = "red") +
   xlab("Number of Solar Panels Produced") +
  ylab("Manufactoring Costs")+
  ggtitle("Real Data and CI: Manufactoring Costs per Units Produced")+
  theme_light()
```

```{r}
# CI lower bound of average manufacturing cost per solar panel for 4700, 4800, 4900 and 5000:
mean(panels_pred$lower[47:50])

# CI upper bound of average manufacturing cost per solar panel for 4700, 4800, 4900 and 5000:
mean(panels_pred$upper[47:50])
```
In conclusion, yes by the time Heliotronics will start manufacturing the 400 panels for canton Tessin the costs per unit will already have decreased. The average unit cost for those 400 units is $688.8399.
Compared to the initial average unit cost of $901.0591 that Heliotronics observed in the first quarter of 2022.




